That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-23 ms.tex
finished results

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.  The best was $445  < X < 569$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.

@@

\subsection{Background Subtraction} 
\label{sec:background}
The star Kepler-1625 is faint (H mag = 14.0) relative to most other exoplanet host stars observed with WFC3, which makes accurate background subtraction especially important for this target. Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.  We identified several uncontaminated regions by eye: $130 < X < 215$ and $6 < Y  < 24$;  $220 < X < 250$ and $110 < X < 155$; $6 < X < 47$ and $127 < Y < 141$, where $X$ and $Y$ are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).  To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation (MAD) of the pixel counts in these three regions. The per pixel uncertainty due to background subtraction is 1.4826 times the MAD.

@@

To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$. To fit the visit-long trend, we used a linear combination of $X$ and $Y$ position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).  In sum, for exposure number $i$, the systematics model is:
\begin{equation}
\label{eq:sys}
S_i = c_{j}\times(1 + aX_i + bY_i) 
\end{equation}
where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.

@@

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and confirmed that the results from the first half were consistent with the second half.

@@

We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality. The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days. This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$). According to the Bayesian information criterion \citep[BIC;][]{kass95}, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$, which constitutes strong evidence against the inclusion of a moon.  In addition, the moon transit time is not well-constrained by the data. As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.  The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.

\subsection{Comparison with Teachey \& Kipping (2018)}
For comparison, we also fit the raw TK18 data using the no-moon and moon models (best fits shown in Figure\,\ref{fig:bestfit}).  We tested the same detrending model described above (decorrelation with the spectrum's $X$ and $Y$ position), but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We used a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.

Our results are consistent with those presented in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$). The posterior distribution for the moon radius is $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and the moon transit time is centered on $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}).

Compared to fits to our data, the fits to the TK18 data have a larger rms. Notably, the moon model fit to the TK18 data has a larger rms than the no-moon fit to our data (363.4 versus 362.2 ppm), even though it has four additional free parameters. This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon model.  We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.

\begin{figure*}
\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
    \caption{Best fit models compared to transit light curves from this work (left) and from TK18 (right). The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red). The lower left of each panel indicates the fit rms (in ppm), the ${\chi_2}$, the degrees of freedom, and the change in GIC relative to the lowest value. The dotted gray line marks the possible moon ingress identified by TK18.}
\label{fig:bestfit}
\end{figure*}

>>>>

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.  The best was $445  < \mathrm{X} < 569$, and $517 < \mathrm{Y} < 531$, where X and Y are physical pixels in the spectral and spatial direction, respectively.

@@

\subsection{Background Subtraction} 
\label{sec:background}
The star Kepler-1625 is faint (H mag = 14.0) relative to most other exoplanet host stars observed with WFC3, which makes accurate background subtraction especially important for this target. Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.  We identified several uncontaminated regions by eye: $130 < \mathrm{X} < 215$ and $6 < \mathrm{Y}  < 24$;  $220 < \mathrm{X} < 250$ and $110 < \mathrm{X} < 155$; $6 < \mathrm{X} < 47$ and $127 < \mathrm{Y} < 141$, where X and Y are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).  To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation (MAD) of the pixel counts in these three regions. The per pixel uncertainty due to background subtraction is 1.4826 times the MAD.

@@

To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$. To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).  In sum, for exposure number $i$, the systematics model S is:
\begin{equation}
\label{eq:sys}
    \mathrm{S}_i = c_{j}\times(1 + a\mathrm{X}_i + b\mathrm{Y}_i) 
\end{equation}
where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.

@@

\begin{figure*}
\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
    \caption{Best fit models compared to normalized transit light curves from this work (left) and from TK18 (right). The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red). The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.  Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).  The dotted gray line marks the possible moon ingress identified by TK18.}
\label{fig:bestfit}
\end{figure*}

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  We determined the best fit model parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.  The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps. We discarded the first 20\% of the MCMC chain as burn-in. As a quick test for convergence, we divided the remainder of the chain in half and confirmed that the results from the first half were consistent with the second half.

@@

We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality. The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days. This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$). According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$. This constitutes strong evidence against the inclusion of a moon \citep{kass95}.  In addition, the moon transit time is not well-constrained by the data. As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.  The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.

\subsection{Comparison with Teachey \& Kipping (2018)}
\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the results findings here.  To make a direct comparison with their results, we fit the raw TK18 data directly.

We fit the data with both the no-moon and models.  For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).  We therefore opted to use a TK18 systematics model to enable a fair comparison between our results. We used a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model. This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}. Figure\,\ref{fig:bestfit} shows the best fit models.

Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction. The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data). As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.  This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.  
%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.

The moon model also yields qualitatively different posterior distributions for the two data sets.  For the TK18 data, the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}). By contrast, the fit to the new data only yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.

%Our results are consistent with those originally published in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$). The posterior distribution for

%We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.
